\documentclass[a4paper,10pt]{article}

\usepackage{textcomp} % text version of symbols in TS1, e.g. \textrightarrow{}
\usepackage{amstext} % proper support of frequently used \text{} command

\usepackage[left=0.7in,top=1.2in,right=0.9in,bottom=1in]{geometry} % Document margins
\usepackage{color}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref} % Required for adding links	and customizing them

\newcommand{\inspireurl}[1]{\\\href{#1}{INSPIRE-HEP entry}}

\pagestyle{empty} % Removes page numbering
\setlength{\parindent}{0in} % to remove the tab at the beginning of each paragraph

\newcommand{\itab}{\hspace*{-2em}}
\newcommand{ \tab}{\hspace*{ 2em}}
\newcommand{\ihalftab}{\hspace*{-1em}}
\newcommand{ \halftab}{\hspace*{ 1em}}

\newcounter{counter}
\setcounter{counter}{1} % set the counter to 1
%\newcounter{subcounter}[counter] %If you want the subcounter to be reset to zero every time counter is increased
%\addtocounter{counter}{1}
%\arabic{counter}
\newcommand{\mycount}[0]{\arabic{counter}\addtocounter{counter}{1}}

\newcommand{\miniLeft}[1]{\begin{minipage}[t]{0.15\textwidth} {#1} \end{minipage}}
\newcommand{\miniRight}[1]{\begin{minipage}[t]{0.85\textwidth} {#1} \end{minipage} \\}
\newcommand{\mini}[2]{\miniLeft{#1} \miniRight{#2}}
\newcommand{\Publications}[1]{\miniLeft{\begin{center} [\mycount] \end{center}}  \miniRight{#1} \\}

\newcommand{\Section}[1]{\linethickness{0.8mm} \textcolor{blue}{\\ {\textbf{#1}} \vspace{-3mm} \\  \line(1,0){250}} 
\\ } 


\begin{document}

%--------------------------------------
%	NAME AND CONTACT INFORMATION
%--------------------------------------

\vspace{-.1cm}
\par{\centering\textcolor{blue}{ \underline{CURRICULUM VITAE}\\}} % CURRICULUM VITAE

%\textcolor{cyan}{\large CURRICULUM VITAE\\} % CURRICULUM VITAE

\vspace{0.7cm} % vertical distance

%======================================
%\Section{Contact Information}

{\large \textbf{Javad Komijani}} \\

\vspace{-5mm}
\begin{minipage}[t]{0.40\textwidth} 
{\ }\\
%{jkomijani\_\_\_at\_\_\_physics.wustl.edu}
{jkomijani\_\_\_at\_\_\_ut.ac.ir}
\end{minipage}
\begin{minipage}[t]{0.60\textwidth} 
\begin{flushright}
{ }
%{School of Physics and Astronomy}\\
%{University of Glasgow, UK}
\end{flushright}
\end{minipage} \\

\vspace{0.5cm} % vertical distance

%======================================
\Section{Education and Research Experience}

% fourth postdoc 
% \mini{2021}{{Postdoctoral Researcher}, \textbf{ETH Z\"urich}}

% third postdoc 
\mini{2019-2020}{{Postdoctoral Researcher}, \textbf{University of Tehran}}

% second postdoc 
\mini{2017-2018}{{Postdoctoral Researcher}, \textbf{University of Glasgow}}

% first postdoc 
\mini{2015-2017}{{Postdoctoral Researcher}, \textbf{Technical University of Munich}}

% Ph.D.
\mini{2010-2015}{{Ph.D. in Physics}, \textbf{Washington University in St. Louis}}
\mini{Thesis Title}{Topics in Lattice Gauge Theory and Theoretical Physics}
\mini{Advisors}{Prof. Claude Bernard and Prof. Carl M. Bender}

% M.Sc.
\mini{2006-2009}{{M.Sc. in Electrical Engineering}, \textbf{University of Tehran}}
%\mini{Thesis Title}{Green's Functions for Structures Involving a PEMC Ground}
%\mini{Advisor}{Prof. Jalil Rashed-Mohassel}

% B.Sc.
\mini{2002-2006}{{B.Sc. in Electrical Engineering}, \textbf{University of Tehran}}


%======================================
\Section{Teaching Experience}

\mini{Fall 2019}{\emph{Workshop on Lattice QCD (with Monte Carlo Simulations)}, Instructor, University of Tehran}\\
\mini{Winter 2018}{\emph{C Programing under Linux}, Teaching Assistant, University of Glasgow}\\
\mini{Spring 2016}{\emph{Elementary Particle Physics}, Teaching Assistant, Technical University of Munich }\\
\mini{Spring 2016}{\emph{Quantum Mechanics}, Teaching Assistant, Technical University of Munich }\\
\mini{Fall 2015}{\emph{Quantum Field Theory}, Teaching Assistant, Technical University of Munich }\\
\mini{Spring 2015}{\emph{Statistical Mechanics}, Teaching Assistant, Washington University in St. Louis}\\
\mini{Fall 2013}{\emph{Quantum Mechanics}, Teaching Assistant, Washington University in St. Louis}\\
\mini{Fall 2012}{\emph{Physics I}, Teaching Assistant, Washington University in St. Louis}\\
\mini{Spring 2011}{\emph{Physics II}, Teaching Assistant, Washington University in St. Louis}\\
\mini{Spring 2011}{\emph{Special Relativity}, Teaching Assistant, Washington University in St. Louis}\\
\mini{Spring 2006}{\emph{Engineering Mathematics}, Teaching Assistant, University of Tehran}\\
\mini{Spring 2006}{\emph{Electronics Lab I}, Teaching Assistant, University of Tehran}\\
\mini{Fall 2005}{\emph{Engineering Mathematics}, Teaching Assistant, University of Tehran}\\ 
\mini{Summer 2005}{\emph{Electronics Lab II}, Teaching Assistant, University of Tehran}


%======================================
% \clearpage
\Section{Computer Skills}

\mini{~}{Python, Cython, C/C++, Bash}\\
\mini{~}{MATLAB, Mathematica}

%======================================
\Section{Public Scripts}
\mini{\href{https://github.com/jkomijani/gauge_tools}{gauge\_tools}}
{A Cython/Python package for Monte Carlo simulations of gauge theories.}

\mini{\href{https://github.com/jkomijani/meson_mass}{meson\_mass}}
{A Python package for mesons masses from lattice-QCD simulations.}

%======================================
\Section{Selected Publications}

\Publications
{ J.~Komijani, P.~Petreczky and J.~H.~Weber,
  {``Strong coupling constant and quark masses from lattice QCD,''}
  \textit{Prog. Part. Nucl. Phys.~113, 103788 (2020)}
  [arXiv:2003.11703]
  \inspireurl{http://inspirehep.net/record/1788480}
}

% \Publications
% { L.~J.~Cooper \textit{et al.},
%   {``$B_c \to B_{s(d)}$ form factors from lattice QCD,''}
%   \textit{Phys.~Rev. D~102, 014513 (2020)}
%   [arXiv:2003.00914]
%   \inspireurl{http://inspirehep.net/record/1783324}
% }

\Publications
{ C.M.~Bender, J. Komijani, Q. Wang,
  {``Nonlinear eigenvalue problems for generalized Painlev\'e equations,''}
  \href{https://doi.org/10.1088/1751-8121/ab2bcc}{
  \textit{J.~Phys.~A: Math. and Theor.~52, 315202 (2019)}} [arXiv:1903.10640]
}

\Publications 
{ C.T.H.~Davies {\it et al.},
  {``Determination of the quark condensate from heavy-light current-current correlators in full lattice QCD,''}
  \textit{Phys.~Rev. D~100, 034506 (2019)}
  [arXiv:1811.04305]
  \inspireurl{http://inspirehep.net/record/1703119}
} 


\Publications 
{ A.~Bazavov {\it et al.},
  {``Up-, down-, strange-, charm-, and bottom-quark masses from four-flavor lattice QCD,''}
  \textit{Phys.~Rev. D~98, 054517 (2018)}
  [arXiv:1802.04248]
  \inspireurl{http://inspirehep.net/record/1654552}
}

\Publications 
{ A.~Bazavov {\it et al.},
  {``$B$- and $D$-meson leptonic decay constants from four-flavor lattice QCD,''}
  \textit{Phys.~Rev. D~98, 074512 (2018)}
  [arXiv:1712.09262]
  \inspireurl{http://inspirehep.net/record/1644910}
}

\Publications
{ N.~Brambilla , J.~Komijani, A.S.~Kronfeld, A.~Vairo,
  {``Relations between Heavy-light Meson and Quark Masses,''}
  \textit{Phys.~Rev. D~97, 034503 (2018)}
  [arXiv:1712.04983]
  \inspireurl{http://inspirehep.net/record/1643281}
}
 
\Publications 
{ J.~Komijani,
  {``A discussion on leading renormalon in the pole mass,''}
  \textit{JHEP 1708, 062 (2017)}
  [arXiv:1701.00347]
  \inspireurl{http://inspirehep.net/record/1507484}
}

\Publications
{ C.M.~Bender and J.~Komijani, 
  {``Painlev\'e Transcendents and ${\mathcal{P}}{\mathcal{T}}$-Symmetric Hamiltonians,''}
  \href{https://doi.org/10.1088/1751-8113/48/47/475202}{
  \textit{J.~Phys.~A: Math. and Theor. 48, 475202 (2015)}}
  [arXiv:1502.04089]
  %\inspireurl{http://inspirehep.net/record/1344799}
}
 
\Publications
{ A.~Bazavov {\it et al.},
  {``Charmed and light pseudoscalar meson decay constants from four-flavor lattice QCD with physical light quarks,''}
  \textit{Phys.~Rev. D~90, 074509 (2014)}
  [arXiv:1407.3772]
  \inspireurl{http://inspirehep.net/record/1306303}
}

\Publications
{ C.M.~Bender, A.~Fring and J.~Komijani,
  {``Nonlinear Eigenvalue Problems,''}
  \href{https://doi.org/10.1088/1751-8113/47/23/235204}{
  \textit{J.~Phys.~A: Math. and Theor.~47, 235204 (2014)}}
  [arXiv:1401.6161]
}

\Publications
{ C.~Bernard and J.~Komijani, 
  {``Chiral Perturbation Theory for All-Staggered Heavy-Light Mesons,''}
  \textit{Phys.~Rev. D~88, 094017 (2013)}
  [arXiv:1309.4533]
  \inspireurl{http://inspirehep.net/record/1254568}
}

%======================================
% \pagebreak
\Section{References}

\begin{minipage}[t]{0.25\textwidth}
\textbf{Claude Bernard}
\end{minipage} \begin{minipage}[t]{0.75\textwidth} 
Washington University in St. Louis, \textcolor{blue}{cb\_\_\_at\_\_\_lump.wustl.edu}
\end{minipage} \\

\begin{minipage}[t]{0.25\textwidth}
\textbf{Carl M. Bender}
\end{minipage} \begin{minipage}[t]{0.75\textwidth} 
Washington University in St. Louis, \textcolor{blue}{cmb\_\_\_at\_\_\_wustl.edu}
\end{minipage} \\

\begin{minipage}[t]{0.25\textwidth}
\textbf{Andreas S. Kronfeld}
\end{minipage} \begin{minipage}[t]{0.75\textwidth} 
Fermi National Accelerator Laboratory, \textcolor{blue}{ask\_\_\_at\_\_\_fnal.gov}
\end{minipage} \\ 

\begin{minipage}[t]{0.25\textwidth}
\textbf{Doug Toussaint}
\end{minipage} \begin{minipage}[t]{0.75\textwidth} 
University of Arizona, \textcolor{blue}{doug\_\_\_at\_\_\_physics.arizona.edu}
\end{minipage} \\ 

\begin{minipage}[t]{0.25\textwidth}
\textbf{Nora Brambilla}
\end{minipage} \begin{minipage}[t]{0.75\textwidth} 
Technical University of Munich, \textcolor{blue}{nora.brambilla\_\_\_at\_\_\_ph.tum.de}
\end{minipage} \\ 

\begin{minipage}[t]{0.25\textwidth}
\textbf{Christine Davies}
\end{minipage} \begin{minipage}[t]{0.75\textwidth} 
University of Glasgow, \textcolor{blue}{Christine.Davies\_\_\_at\_\_\_glasgow.ac.uk}
\end{minipage} \\ 
 
\begin{minipage}[t]{0.25\textwidth}
\textbf{Sedigheh Deldar}
\end{minipage} \begin{minipage}[t]{0.75\textwidth} 
University of Tehran, \textcolor{blue}{sdeldar\_\_\_at\_\_\_ut.ac.ir}
\end{minipage} \\

\end{document}
