\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}

\begin{document}

\begin{center}
\textbf{\Large Javad Komijani} \\
Zurich, Switzerland \\
\href{mailto:jkomijani@gmail.com}{jkomijani at gmail.com}  $|$  +41767969992 $|$ \href{https://www.linkedin.com/in/javad-komijani-543a31235}{LinkedIn} $|$ \href{https://jkomijani.github.io/}{Personal webpage}
\end{center}

\section*{Professional Summary}

Highly analytical and detail-oriented researcher with a strong background in computational and theoretical physics, statistical analysis, and machine learning. Holding an MSc in Electrical Engineering and a PhD in Physics, with extensive experience in numerical simulations and data-driven research. Passionate about applying data science and machine learning techniques to solve complex real-world problems.

\section*{Education}

\begin{itemize}

\item
\textbf{PhD in Physics}:
Washington University in St. Louis, 2015

Thesis: Topics in Lattice Gauge Theory and Theoretical Physics

\begin{itemize}
\item Development of theoretical models based on effective field theories,
\item Applied Bayesian inference to analyze lattice QCD data,
\item Estimation of parameters of the Standard Model of Particle Physics,
\item Introduction of new concepts in mathematical physics
\end{itemize}

\item
\textbf{MSc in Electrical Engineering}:
University of Tehran, 2009

Focus: Wave propagation, signal processing, statistical analysis

\end{itemize}

\section*{Technical Skills}
\begin{itemize}
\item \textbf{Programming \& Tools}: Python, Cython, C/C++, MATLAB, Mathematica, PyTorch, Pandas, NumPy, SciPy, Scikit-learn
\item \textbf{Machine Learning \& AI}: Generative Models, Diffusion Models, Normalizing Flows
\item \textbf{Mathematical \& Statistical Methods}: Bayesian Inference, Monte Carlo Methods, Statistical Analysis, Optimization
\item \textbf{Computational Methods}: Numerical Simulations, High-Performance Computing (HPC)
\end{itemize}

\section*{Work \& Research Experience}

\begin{itemize}

\item
\textbf{Postdoctoral \& Senior Postdoctoral Researcher}:  ETH Zurich, 2021 -- Present

\begin{itemize}
\item Developed and implemented machine learning algorithms for generating lattice field configurations
\item Worked with HPC systems in lattice-QCD simulations
\item Collaborated with international teams on computational and theoretical research projects
\item Supervised and mentored PhD and Master students
\item Participated in teaching Quantum Mechanics at ETH Zurich
\end{itemize}

\item
\textbf{Postdoctoral Researcher}:\\
University of Tehran, 2019 -- 2020\\
University of Glasgow, 2017 -- 2018\\
Technical University of Munich, 2015 -- 2017

\begin{itemize}
\item Determination of parameters of the Standard Model of Particle Physics, such as the masses of quarks and various decay constants and form factors, by lattice-QCD computations, theoretical modeling, and statistical analysis
\end{itemize}

\end{itemize}

\section*{Selected Publications \& Conference Proceedigs}

\begin{itemize}
\item J.~Komijani, M.~K.~Marinkovic, ``Normalizing flows for SU(N) gauge theories employing singular value decomposition,'' [arXiv:2501.18288]. \href{https://inspirehep.net/literature/2874143}{InspireHEP}

\item J.~Komijani, M.~K.~Marinkovic, ``Generative models for scalar field theories: how to deal with poor scaling?,'' [arXiv:2301.01504]. \href{https://inspirehep.net/literature/2620105}{InspireHEP}

\item J.~Komijani, ``First-order nonlinear eigenvalue problems involving functions of a general oscillatory behavior,'' \textit{J.~Phys.~A: Math. and Theor.~54, 465202 (2021)} [arXiv:2107.02475].

\item J.~Komijani, P.~Petreczky and J.~H.~Weber, ``Strong coupling constant and quark masses from lattice QCD,'' \textit{Prog. Part. Nucl. Phys.~113, 103788 (2020)} [arXiv:2003.11703].

\item C.M.~Bender, J. Komijani, Q. Wang, ``Nonlinear eigenvalue problems for generalized Painlev\'e equations,'' \textit{J.~Phys.~A: Math. and Theor.~52, 315202 (2019)} [arXiv:1903.10640].

\item C.T.H.~Davies \textit{et al.}, ``Determination of the quark condensate from heavy-light current-current correlators in full lattice QCD,'' \textit{Phys.~Rev. D~100, 034506 (2019)} [arXiv:1811.04305]. \href{http://inspirehep.net/record/1703119}{InspireHEP}

\item A.~Bazavov \textit{et al.}, ``Up-, down-, strange-, charm-, and bottom-quark masses from four-flavor lattice QCD,'' \textit{Phys.~Rev. D~98, 054517 (2018)} [arXiv:1802.04248]. \href{http://inspirehep.net/record/1654552}{InspireHEP}

\item A.~Bazavov \textit{et al.}, ``$B$- and $D$-meson leptonic decay constants from four-flavor lattice QCD,'' \textit{Phys.~Rev. D~98, 074512 (2018)} [arXiv:1712.09262]. \href{http://inspirehep.net/record/1644910}{InspireHEP}

\item N.~Brambilla , J.~Komijani, A.S.~Kronfeld, A.~Vairo, ``Relations between Heavy-light Meson and Quark Masses,'' \textit{Phys.~Rev. D~97, 034503 (2018)} [arXiv:1712.04983]. \href{http://inspirehep.net/record/1643281}{InspireHEP}

\item J.~Komijani, ``A discussion on leading renormalon in the pole mass,'' \textit{JHEP 1708, 062 (2017)} [arXiv:1701.00347]. \href{http://inspirehep.net/record/1507484}{InspireHEP}

\item C.M.~Bender and J.~Komijani, ``Painlev\'e Transcendents and ${\mathcal{P}}{\mathcal{T}}$-Symmetric Hamiltonians,'' \textit{J.~Phys.~A: Math. and Theor. 48, 475202 (2015)} [arXiv:1502.04089].

\item A.~Bazavov \textit{et al.}, ``Charmed and light pseudoscalar meson decay constants from four-flavor lattice QCD with physical light quarks,'' \textit{Phys.~Rev. D~90, 074509 (2014)} [arXiv:1407.3772]. \href{http://inspirehep.net/record/1306303}{InspireHEP}

\item C.M.~Bender, A.~Fring and J.~Komijani, ``Nonlinear Eigenvalue Problems,'' \textit{J.~Phys.~A: Math. and Theor.~47, 235204 (2014)} [arXiv:1401.6161].

\item C.~Bernard and J.~Komijani, ``Chiral Perturbation Theory for All-Staggered Heavy-Light Mesons,'' \textit{Phys.~Rev. D~88, 094017 (2013)} [arXiv:1309.4533]. \href{http://inspirehep.net/record/1254568}{InspireHEP}
\end{itemize}

\end{document}

